Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-08 article.tex
correction : some typo
add : definition of set X and Y \n modification : the presentation of the problem of bivincular and LCS

\newcommand{\x}{X}
\newcommand{\y}{Y}
\newcommand{\bmotif}{(\sigma,\x,\y)}

@@

@@

A \emph{bivincular pattern} (abbreviated BVP) $\sigma$
of length $k$ is a permutation in $S_k$ written in
two-line notation 
(that is the top row is $12\,\ldots\,k$ and the bottom row
is a permutation $\sigma_1\sigma_2\,\ldots\,\sigma_k$).
We have the following conditions on the top and bottom rows
of $\sigma$:
\begin{itemize}
	\item
	If the bottom line of $\sigma$ contains
	$\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$
	then the letters corresponding to 
	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
	$\sigma$ in a permutaton must be adjacent, whereas there is
	no adjacency condition for
	non-underlined consecutive letters.
	Moreover if the bottom row of $\sigma$ begins with
	$_\llcorner{\sigma_1}$ then any occurrence of $\sigma$ 
	in a permutation $\pi$ must begin with the leftmost 
	letter of $\pi$,
	and 
	if the bottom row of $\sigma$ begins with
	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$ 
	in a permutation $\pi$ must end with the rightmost 
	letter of $\pi$.
	\item
	If the top line of $\sigma$ contains
	$\overline{i\,i+1\,\ldots\,j}$ then the letters corresponding to
	$\sigma_i, \sigma_{i+1}, \ldots, \sigma_j$ in an
	occurrence of $\sigma$ in a permutation must be adjacent in values,
	whereas there is no value adjacency restriction for non-overlined 
	letters.
	Moreover, if the top row of $\sigma$ begins with
	$^\ulcorner{1}$ then
	any occurrence of $\sigma$ is a permutation $\pi$ must begin with
	the smallest letter of $\pi$, and
	if top row of $\sigma$ ends with $k^\urcorner$ then
	any occurrence of $\sigma$ is a permutation $\pi$ must end with
	the largest letter of $\pi$.
\end{itemize}
% A bivincular pattern avoids a set of permutations $P$ if its bottom
% row $\sigma_1\sigma_2\,\ldots\,\sigma$ avoids every permutation in $P$.

@@

\begin{proof} 
	The forward direction is obvious.
	We prove the backward direction by induction on the size of the motif
	$\sigma$.
	The base case is a motif of size 2. Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$. Let's $t$ be a subsequence of $\ptext$ such that $\stripew{t}$ is a occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$. Because we have $\stripe{t}{1}=\ustep$, so the next element of $t[1]$ in $\ptext$ is superior to  $t[1]$, so we have a match. Same idea goes of motif $(21)$.
	Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$. Suppose that we have a subsequence $t$ of $\ptext$ such that $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$, then $\stripew{t[2:]}$ is an occurrence of $\pmotif[2:]$ in $\ptext$. Moreover
	$\pmotif[2:] \in \Av{n}{(231,213)}$ so by hypothesis of induction $t[2:]$ is an occurrence of $\sigma[2:]$ in $\ptext$.
	Moreover if $\stripe{\pmotif}{1}$ is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} $\pmotif[1]$ is the minimal (maximal) element of the motif. Furthermore $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$ , so $\stripe{t}{1}$ is also ascend (descent) thus $t[1]$ is also the minimal (maximal) element of the subsequence $t$ which complete our proof.

@@

This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.

			\begin{proposition}
			Let $\bmotif$ be a bivincular motif 
			avoiding (231,213), 
			$\ptext$ a permutation,
			we can decide in $O(|\pmotif||\ptext|^3)$ time
			and $O(|\ptext|^3)$ space
			if $\pmotif$ 
			appear in $\ptext$.
			\end{proposition}

@@

			Given a bivincular motif $\bmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\

			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \left\{ 
				\begin{array}{l l}
					true & \text{If $\pmotif[i:]$ is a motif of $\ptext[j:]$}\\
						& \text{with every element in}\\ 
						&[\min,\max]\\

@@

			$\mathbb{P}_{\pmotif,\ptext,\min,\max}$ is closed under induction. 
			it can be
			solved by means of the following relations:\\

@@

			if $n_\pmotif \notin  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\

			if $n_\pmotif \notin  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						and }\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						and }\\
						&\text{$\ptext[n_\ptext]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(n_\pmotif+1,n_\ptext)= true $\\

			\textbf{STEP :} \\		
			$\mathbb{P}_{\bmotif,\ptext,\min,\max}(i,j)= \\ \left\{ 
					\begin{array}{l l}

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $\min<\ptext[j]<\max$} \\		
						&\\

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\

@@

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,\ptext^{-1}[\ptext[j]+1]) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,\ptext^{-1}[\ptext[j]-1]) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\ptext[j],\max}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\bmotif,\ptext,\min,\ptext[j]}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

@@

	$S_{\pi_1,\pi_2}(\min_1,\max_1,\min_2,\min_2,i_1,i_2)$
	= max$\{$ $|s|$ $|$ 
	s is a pattern occurring 
	in  $\pi_1[i_1:]$
	by the subsequence $s_1$ and $\min(s_1)=\min_1$ and $\max(s_1)=\max_1$
	and s is occurring
	in  $\pi_2[i_2:]$
	by the subsequence $s_2$ and $\min(s_2)=\min_2$ and $\max(s_2)=\max_2$	
	$\}$\\

@@

	\textbf{BASE :} \\
	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(|\pi_1|,|\pi_2|) = \left\{ 
			\begin{array}{l l}
				1 & \text{if $\min_1=\pi_1[j]=\max_1$  
				}\\
				& \text{ and $\min_2=\pi_2[j]=\max_2$}\\
				0 & otherwise\\
			\end{array} \right. $\\

@@

	$S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2) =$\\
	\indent $ \max \left\{ 
			\begin{array}{l l}
				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2+1) \\
				S_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_22}(i_1+1,i_2) \\
				S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)
			\end{array} \right. $\vspace{20pt}\\

	with 
	$S'_{\pi_1,\pi_2,\min_1,\max_1,\min_2,\max_2}(i_1,i_2)=\\ \left\{ 
				\begin{array}{l l}
					1+S_{\pi_1,\pi_2,\pi_1[i_1],\max_1,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]<\min_1$ } \\
					& \text{and $\pi_2[i_2]<\min_2$} \\
					&\\
					1+S_{\pi_1,\pi_2,\min_1,\pi_1[i_1],\min_2,\pi_2[i_2]}(i_1+1,i_2+1)  & \text{$\pi_1[i_1]>\max_1$ } \\	
					&\text{and $\pi_2[i_2]>\max_2$}\\	
					&\\	
					0 & \text{otherwise}\\							
				\end{array} \right.$\\

>>>>

@@

%binvincular 
\newcommand{\x}{X}
\newcommand{\y}{Y}
\newcommand{\bmotif}{(\sigma,\x,\y)}

\newcommand{\pbmotif}{\pmotif^+}
\newcommand{\pbmotifX}{\x_{\pbmotif}}
\newcommand{\pbmotifY}{\y_{\pbmotif}}

%LSC
\DeclareMathOperator{\LCSa}{LCS}
\newcommand{\LCS}[8]{\LCSa_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}

\DeclareMathOperator{\matcha}{MATCH}
\newcommand{\match}[8]{\matcha_{{#1},{#2},{#3}}^{{#4},{#5},{#6}}({#7},{#8})}

@@

A \emph{bivincular pattern} (abbreviated BVP) $\sigma$
of length $k$ is a permutation in $S_k$ written in
two-line notation 
(that is the top row is $12\,\ldots\,k$ and the bottom row
is a permutation $\sigma_1\sigma_2\,\ldots\,\sigma_k$).
We have the following conditions on the top and bottom rows
of $\sigma$:
\begin{itemize}
	\item
	If the bottom line of $\sigma$ contains
	$\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$
	then the letters corresponding to 
	$\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j$ in an occurrence of
	$\sigma$ in a permutaton must be adjacent, whereas there is
	no adjacency condition for
	non-underlined consecutive letters.
	Moreover if the bottom row of $\sigma$ begins with
	$_\llcorner{\sigma_1}$ then any occurrence of $\sigma$ 
	in a permutation $\pi$ must begin with the leftmost 
	letter of $\pi$,
	and 
	if the bottom row of $\sigma$ begins with
	${\sigma_k}_\lrcorner$ then any occurrence of $\sigma$ 
	in a permutation $\pi$ must end with the rightmost 
	letter of $\pi$.
	\item
	If the top line of $\sigma$ contains
	$\overline{i\,i+1\,\ldots\,j}$ then the letters corresponding to
	$\sigma_i, \sigma_{i+1}, \ldots, \sigma_j$ in an
	occurrence of $\sigma$ in a permutation must be adjacent in values,
	whereas there is no value adjacency restriction for non-overlined 
	letters.
	Moreover, if the top row of $\sigma$ begins with
	$^\ulcorner{1}$ then
	any occurrence of $\sigma$ is a permutation $\pi$ must begin with
	the smallest letter of $\pi$, and
	if top row of $\sigma$ ends with $k^\urcorner$ then
	any occurrence of $\sigma$ is a permutation $\pi$ must end with
	the largest letter of $\pi$.
\end{itemize}
Given a motif $\pmotif$ we represent the elements underlined by the set $\x$. An index $i$ of an element is in $\x$ if and only if $i$ and $i+1$ need to be adjacent ($\pmotif[i]$ and $\pmotif[i+1]$ are underlined).
For example if we have $\underline{\sigma_i\sigma_{i+1}\,\ldots\,\sigma_j}$, then ${i,i+1,\ldots,j-1} \in \y$. 
We represent the index that need to be overlined by the set $\y$. An index $i$ is in $\y$ if and only if $i$ and $i+1$ need to be adjacent ($i$ and $i+1$ are overlined).
For example if we have
For example if we have $\overline{i\,i+1\,\ldots\,j}$, then ${i,i+1,\ldots,j-1} \in \y$.
% A bivincular pattern avoids a set of permutations $P$ if its bottom
% row $\sigma_1\sigma_2\,\ldots\,\sigma$ avoids every permutation in $P$.

@@

\begin{proof} 
	The forward direction is obvious.
	We prove the backward direction by induction on the size of the motif
	$\sigma$.
	The base case is a motif of size 2. Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$. Let's $t$ be a subsequence of $\ptext$ such that $\stripew{t}$ is a occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$. Because we have $\stripe{t}{1}=\ustep$, the next element of $t[1]$ is $\ptext$ is superior to  $t[1]$, so we have a match. Same idea goes of motif $(21)$.
	Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$. Suppose that we have a subsequence $t$ of $\ptext$ such that $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$, then $\stripew{t[2:]}$ is an occurrence of $\pmotif[2:]$ in $\ptext$. Moreover
	$\pmotif[2:] \in \Av{n}{(231,213)}$ so by hypothesis of induction $t[2:]$ is an occurrence of $\sigma[2:]$ in $\ptext$.
	Moreover if $\stripe{\pmotif}{1}$ is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} $\pmotif[1]$ is the minimal (maximal) element of the motif. Furthermore $\stripew{t}$ is an occurrence of $\stripew{\pmotif}$ in $\stripew{\ptext}$ , so $\stripe{t}{1}$ is also ascend (descent) thus $t[1]$ is also the minimal (maximal) element of the subsequence $t$ which complete our proof.

@@

This section gives an algorithm to detect bivincular permutation in polynomial time in the case where the motif avoid $(213,231)$.
We denote $\pbmotif=\bmotif$ the bivincular motif.

\begin{proposition}
Let $\pbmotif$ be a bivincular motif such that $\pmotif$
avoid (231,213), 
$\ptext$ a permutation,
we can decide in $O(|\pmotif||\ptext|^3)$ time
and $O(|\ptext|^3)$ space
if $\pbmotif$
appear in $\ptext$.
\end{proposition}

@@

			Given a bivincular motif $\pbmotif$ with $\pmotif \in \Av{n_\pmotif}{231,213} $, and a text $\ptext \in \Av{n_\ptext}{231,213}$, $i$,$j$ , $i<j$.\\

			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \left\{ 
				\begin{array}{l l}
					true & \text{If $\pbmotif[i:]$ is a motif of $\ptext[j:]$}\\
						& \text{with every element in}\\ 
						&[\min,\max]\\

@@

			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}$ is closed under induction. 
			it can be
			solved by means of the following relations:\\

@@

			if $n_\pmotif \notin  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x $
			and $n_\pmotif \notin  \y$ : \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

			if $n_\pmotif \notin  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,j)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[j]<\max$
						and }\\
						&\text{$\ptext[j]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,j)= true $\\

			if $n_\pmotif \in  \x$  
			and $n_\pmotif \in  \y$ 
			and $\pmotif[n_\pmotif]$ is the maximal element: \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif,n_\ptext)= \left\{ 
					\begin{array}{l l}
						true & \text{if $\min<\ptext[n_\ptext]<\max$
						and }\\
						&\text{$\ptext[n_\ptext]$ is the maximal element}\\
						false & otherwise\\
					\end{array} \right. $\\	
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(n_\pmotif+1,n_\ptext)= true $\\

			\textbf{STEP :} \\		
			$\mathbb{P}_{\pbmotif,\min,\max}^{\ptext}(i,j)= \\ \left\{ 
					\begin{array}{l l}

						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$
							and $i \notin \x$}\\
							& \text{and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\bigcup_{j<k}\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,k) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \notin \x$ and $i \notin \y$  }\\
							& \text{and $\min<\ptext[j]<\max$} \\		
						&\\

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\ustep$}\\
							& \text{and $i \in \x$ and $i \notin \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1) 
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							& \text{and $i \in \x$ and $i \notin \y$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\

@@

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]+1]) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \notin \x$ and $i \in \y$}\\
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]+1]>j$}\\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,\ptext^{-1}[\ptext[j]-1]) 
							&\text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \notin \x$ and $i \in \y$ }\\	
							& \text{and $\min<\ptext[j]<\max$} \\
							&\text{and $\ptext^{-1}[\ptext[j]-1]>j$}\\
						&\\

						\mathbb{P}_{\pbmotif,\ptext[j],\max}^{\ptext}(i+1,j+1) 
							&\text{if $\stripe{\pmotif}{i}=\ustep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]+1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\

						\mathbb{P}_{\pbmotif,\min,\ptext[j]}^{\ptext}(i+1,j+1)
							& \text{if $\stripe{\pmotif}{i}=\dstep$}\\
							&\text{and $i \in \x$ and $i \in \y$}\\ 
							&\text{and $\ptext[j]-1=\ptext[j+1]$ }\\
							& \text{and $\min<\ptext[j]<\max$} \\
						&\\	
						False & Otherwise\\																		
					\end{array} \right. $\\

@@

	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}$
	= max$\{$ $|s|$ $|$ 
	s is a pattern occurring 
	in  $\pi_1[i_1:]$
	by the subsequence $s_1$ and $\min(s_1)=\min_1$ and $\max(s_1)=\max_1$
	and s is occurring
	in  $\pi_2[i_2:]$
	by the subsequence $s_2$ and $\min(s_2)=\min_2$ and $\max(s_2)=\max_2$	
	$\}$\\

@@

	\textbf{BASE :} \\
	$	\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{|\pi_1|}{|\pi_2|} = \left\{ 
			\begin{array}{l l}
				1 & \text{if $\min_1=\pi_1[j]=\max_1$  
				}\\
				& \text{ and $\min_2=\pi_2[j]=\max_2$}\\
				0 & otherwise\\
			\end{array} \right. $\\

@@

	$\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
	=$
	$ \max \left\{ 
			\begin{array}{l l}
				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2+1} \\
				\\
				\LCS{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1+1}{i_2} \\
				\\
				\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}
			\end{array} \right. $\vspace{20pt}\\

	with
	$\match{\pi_1}{\min_1}{\max_1}{\pi_2}{\min_2}{\max_2}{i_1}{i_2}=\\ \left\{ 
				\begin{array}{l l}
					1+\LCS{\pi_1}{\pi_1[i_1]}{\max_1}{\pi_2}{\pi_2[i_2]}{\max_2}{i_1}{i_2+1} & \text{$\pi_1[i_1]<\min_1$ } \\
					& \text{and $\pi_2[i_2]<\min_2$} \\
					&\\
					1+\LCS{\pi_1}{\min_1}{\pi_1[i_1]}{\pi_2}{\min_2}{\pi_2[i_2]}{i_1+1}{i_2}
					 & \text{$\pi_1[i_1]>\max_1$ } \\	
					&\text{and $\pi_2[i_2]>\max_2$}\\	
					&\\	
					0 & \text{otherwise}\\							
				\end{array} \right.$\\
